### 2015-10-26 paper/main.tex
add more figure plotting rmd files; tidy up size and cropping of pdf

\begin{figure}
\center \includegraphics[height=6in]{../figures/decomp_ZA.pdf}
\caption{Illustration that the unimodal assumption (UA) in \ashr can produce very different results from existing methods.
The figure shows, for a single simulated dataset, the way different methods decompose $p$ values (left) and $z$ scores (right) into a null component (dark blue) and an alternative component (cyan). In the $z$ score space the alternative distribution is placed on the bottom to highlight the differences in its shape among methods.
The three existing methods (\qvalue, \locfdr, \mixfdr) all effectively make the Zero Assumption, which results in a ``hole" in the alternative $z$ score distribution around 0.
In contrast the method introduced here (\ashr) makes the Unimodal Assumption -- that the effect sizes, and thus the $z$ scores, have a unimodal distribution about 0 -- which yields a very different decomposition. (In this case the \ashr decomposition is closer to the truth: the data were simulated under a model where all of the effects are non-zero, so the ``true" decomposition would make everything cyan.)} \label{fig:ZA}
\end{figure}

@@

\begin{figure} 
\begin{center}
\begin{subfigure}{\textwidth}
	\includegraphics[height=1.8in]{../figures/scenarios_density.pdf} 
	\caption{Densities of non-zero effects, $g_1$, used in simulations.} \label{fig:altdens}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=1.8in]{../figures/pi0_est.pdf} 
\caption{Comparison of true and estimated values of $\pi_0$. When the UA holds all methods yield conservative (over-)estimates for $\pi_0$, with \ashr being least conservative, and hence most accurate. When the UA does not hold (``bimodal" scenario) the \ashr estimates are slightly anti-conservative.} \label{fig:pi0sims}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=1.8in]{../figures/lfdr_est.png} 
\caption{Comparison of true and estimated $\lfdr$ from \ashr (ash.n). Black line is $y=x$ and red line is $y=2x$. Estimates of $\lfdr$ are conservative when UA holds, due to conservative estimates of $\pi_0$.} \label{fig:lfdr}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=1.8in]{../figures/lfsr_est.png} 
\caption{As in c), but for $\lfsr$ instead of $\lfdr$. Estimates of $\lfsr$ are consistently less conservative than $\lfdr$ when UA holds, and also less anti-conservative in bimodal scenario.}  \label{fig:lfsr}
\end{subfigure}
\end{center}
\caption{Results of simulation studies (constant precision $s_j=1$).}
\end{figure}

@@

\begin{figure}[h!] 
\begin{subfigure}{\textwidth}
	\includegraphics[height=2in]{../figures/egcdf.pdf}
	\caption{Example estimated cdfs for single data sets compared with truth. The unimodal assumption made by the ash methods effectively regularizes estimates compared with \mixfdr.}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=2in]{../figures/mean_cdf.pdf}
\caption{Average estimated cdfs across $\sim10$ data sets compared with truth; methods here use penalty (\ref{eqn:penalty}) so $\pi_0$ is systematically overestimated.}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=2in]{../figures/mean_cdf_nopen.pdf}
\caption{Average estimated cdfs across $\sim10$ data sets compared with truth; methods here do not use penalty (\ref{eqn:penalty}) so $\pi_0$ is not systematically overestimated. Systematic differences from the truth in ``skew" and ``bimodal" scenarios highlight the effects of model mis-specification.}
\end{subfigure}
\caption{Comparisons of estimated cdfs of $g$ and true cdf of $g$. See Figure \ref{fig:pi0sims} for simulation scenarios.} \label{fig:egcdf}
\end{figure}

@@

\begin{table}[!ht]
\begin{subtable}{\textwidth}
	\centering\input{tables/scoverage_all.tex}
	\caption{All observations. Coverage rates are generally satisfactory, except for the extreme ``spiky" scenario. This is due to the penalty term (\ref{eqn:penalty}) which tends to cause over-shrinking towards zero. Removing this penalty term produces coverage rates closer to the nominal levels for uniform and normal methods (Table \ref{tab:nopen}). Removing the penalty in the half-uniform case is not recommended (see Appendix).}
\end{subtable}

\begin{subtable}{\textwidth}
\centering\input{tables/scoverage_neg.tex}
\caption{``Significant" negative discoveries. Coverage rates are generally satisfactory, except for the uniform-based methods in the spiky and near-normal scenarios,
and the normal-based method in the flat-top scenario. These results likely reflect inaccurate estimates of the tails of $g$ due to a disconnect between the tail of $g$ and the component distributions in these cases. For example, the uniform methods sometimes substantially underestimate the length of the tail of $g$ in these long-tailed scenarios, 
causing over-shrinkage of the tail toward 0.}
\end{subtable}

\begin{subtable}{\textwidth}
\centering\input{tables/scoverage_pos.tex}
\caption{``Significant" positive discoveries. Coverage rates are generally satisfactory, except for the symmetric methods under the asymmetric (``skew") scenario. }
\end{subtable}

@@

\begin{figure}
\begin{subfigure}{\textwidth}
\centering\includegraphics[width=4in]{../figures/GOODPOOReg_hist.pdf} 
    \label{fig:goodpoor-hist}
    \caption{Density histograms of $p$ values for good-precision, poor-precision, and combined observations}
 \end{subfigure}
\begin{subfigure}{\textwidth}
\centering\includegraphics[width=4in]{../figures/GOODPOOReg_scatter.pdf}
    \caption{Comparison of results of different methods applied to good-precision observations only ($x$ axis) and combined data ($y$ axis). Each point shows the ``significance" ($q$ values from \qvalue; $\lfdr$ for \locfdr; $\lfsr$ for \ashr) of a good-precision observation under the two different analyses.} \label{fig:goodpoor-scatter}
\end{subfigure}
\caption{Simulation illustrating how, for existing FDR methods, 
poor-precision observations can contaminate signal from good-precision observations. The top panel (a) illustrates that when 
$p$ values from good-precision observations (left) and from poor-precision observations (center) are combined (right), they produce
a distribution of $p$ values with less overall signal - and so, by conventional methods, will give a higher estimated FDR at any given threshold.
The bottom panel (b) illustrates this behaviour directly for the methods \qvalue and \locfdr: the $q$-values from \qvalue and the $\lfdr$ estimates from \locfdr are higher when applied to all data than when applied to good-precision observations only. In contrast the methods described here (\ashr) produce effectively the same results (here, the lfsr) in the good-precision and combined data analyses.} \label{fig:goodpoor}
\end{figure}

@@

\begin{figure}
\centering\includegraphics[width=4in]{../figures/lfsr_vs_pval_GOODPOOR.pdf}
\caption{Figure illustrating affects of prior assumptions on re-ordering of significance. Left panel shows results under our ``default prior" which assumes that effects $\beta_j$ are identically distributed, independent of $s_j$. Right panel shows results under the ``$p$-value prior", which assumes that $z$ scores $\beta_j/s_j$ are identically distributed, independent of $s_j$.} \label{fig:lfsr_pval}
\end{figure}

@@

\begin{figure}
\begin{center}
\begin{subfigure}{\textwidth}
\includegraphics[height=1.8in]{../figures/lfsr_est_s_nn.png} 
\caption{Comparison of true and estimated $\lfsr$ when data are simulated with no point mass at zero ($\pi_0=0$), and also analyzed by \ashr with no point mass on 0 (and mixture of normal components for $g$). Black line is $y=x$ and red line is $y=2x$. The results illustrate how estimates of $\lfsr$ can be more accurate in this case. That is, assuming there is no point mass can be beneficial if that is indeed true.}  \label{fig:lfsr-nn}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=1.8in]{../figures/lfsr_est_s.png} 
\caption{Comparison of true and estimated $\lfsr$ when data are simulated with point mass at zero (drawn uniformly from [0,1] in each simulation), but analyzed by \ashr with no point mass on 0 (and mixture of normal components for $g$). Black line is $y=x$ and red line is $y=2x$. The results illustrate how estimates of $\lfsr$ can be anti-conservative if we assume there is no point mass when the truth is that there is a point mass.} \label{fig:lfsr-s}
\end{subfigure}
\end{center}
\caption{Illustration of effects of excluding a point mass from the analysis.} \label{fig:lfsr-nopointmass}
\end{figure}

@@

\begin{table}[!ht]
\begin{subtable}{\textwidth}
	\centering\input{tables/scoverage_all_nopen.tex}
	\caption{All observations}
\end{subtable}

\begin{subtable}{\textwidth}
\centering\input{tables/scoverage_neg_nopen.tex}
\caption{``Significant" negative discoveries.}
\end{subtable}

\begin{subtable}{\textwidth}
\centering\input{tables/scoverage_pos_nopen.tex}
\caption{``Significant" positive discoveries.}
\end{subtable}

>>>>

\begin{figure}
\center \includegraphics[height=6in]{figures/decomp_ZA.pdf}
\caption{Illustration that the unimodal assumption (UA) in \ashr can produce very different results from existing methods.
The figure shows, for a single simulated dataset, the way different methods decompose $p$ values (left) and $z$ scores (right) into a null component (dark blue) and an alternative component (cyan). In the $z$ score space the alternative distribution is placed on the bottom to highlight the differences in its shape among methods.
The three existing methods (\qvalue, \locfdr, \mixfdr) all effectively make the Zero Assumption, which results in a ``hole" in the alternative $z$ score distribution around 0.
In contrast the method introduced here (\ashr) makes the Unimodal Assumption -- that the effect sizes, and thus the $z$ scores, have a unimodal distribution about 0 -- which yields a very different decomposition. (In this case the \ashr decomposition is closer to the truth: the data were simulated under a model where all of the effects are non-zero, so the ``true" decomposition would make everything cyan.)} \label{fig:ZA}
\end{figure}

@@

\begin{figure} 
\begin{center}
\begin{subfigure}{\textwidth}
	\includegraphics[width=\textwidth]{../analysis/figure/plot_egdens.Rmd/scenario_density-1.pdf} 
	\caption{Densities of non-zero effects, $g_1$, used in simulations.} \label{fig:altdens}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_pi0est.Rmd/plot_pi0est-1.pdf} 
\caption{Comparison of true and estimated values of $\pi_0$. When the UA holds all methods yield conservative (over-)estimates for $\pi_0$, with \ashr being least conservative, and hence most accurate. When the UA does not hold (``bimodal" scenario) the \ashr estimates are slightly anti-conservative.} \label{fig:pi0sims}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_lfsr.Rmd/plot_lfdr-1.pdf} 
\caption{Comparison of true and estimated $\lfdr$ from \ashr (ash.n). Black line is $y=x$ and red line is $y=2x$. Estimates of $\lfdr$ are conservative when UA holds, due to conservative estimates of $\pi_0$.} \label{fig:lfdr}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_lfsr.Rmd/plot_lfsr-1.pdf} 
\caption{As in c), but for $\lfsr$ instead of $\lfdr$. Estimates of $\lfsr$ are consistently less conservative than $\lfdr$ when UA holds, and also less anti-conservative in bimodal scenario.}  \label{fig:lfsr}
\end{subfigure}
\end{center}
\caption{Results of simulation studies (constant precision $s_j=1$).}
\end{figure}

@@

\begin{figure}[h!] 
\begin{subfigure}{\textwidth}
	\includegraphics[height=2in]{../analysis/figure/plot_cdf_eg.Rmd/egcdf-1.png}
	\caption{Example estimated cdfs for single data sets compared with truth. The unimodal assumption made by the ash methods effectively regularizes estimates compared with \mixfdr.}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=2in]{../analysis/figure/plot_cdf_eg.Rmd/mean_cdf-1.png}
\caption{Average estimated cdfs across $\sim10$ data sets compared with truth; methods here use penalty (\ref{eqn:penalty}) so $\pi_0$ is systematically overestimated.}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=2in]{../analysis/figure/plot_cdf_eg.Rmd/mean_cdf_nopen-1.png}
\caption{Average estimated cdfs across $\sim10$ data sets compared with truth; methods here do not use penalty (\ref{eqn:penalty}) so $\pi_0$ is not systematically overestimated. Systematic differences from the truth in ``skew" and ``bimodal" scenarios highlight the effects of model mis-specification.}
\end{subfigure}
\caption{Comparisons of estimated cdfs of $g$ and true cdf of $g$. See Figure \ref{fig:pi0sims} for simulation scenarios.} \label{fig:egcdf}
\end{figure}

@@

\begin{table}[!ht]
\begin{subtable}{\textwidth}
	\centering\input{../analysis/table/scoverage_all.tex}
	\caption{All observations. Coverage rates are generally satisfactory, except for the extreme ``spiky" scenario. This is due to the penalty term (\ref{eqn:penalty}) which tends to cause over-shrinking towards zero. Removing this penalty term produces coverage rates closer to the nominal levels for uniform and normal methods (Table \ref{tab:nopen}). Removing the penalty in the half-uniform case is not recommended (see Appendix).}
\end{subtable}

\begin{subtable}{\textwidth}
\centering\input{../analysis/table/scoverage_neg.tex}
\caption{``Significant" negative discoveries. Coverage rates are generally satisfactory, except for the uniform-based methods in the spiky and near-normal scenarios,
and the normal-based method in the flat-top scenario. These results likely reflect inaccurate estimates of the tails of $g$ due to a disconnect between the tail of $g$ and the component distributions in these cases. For example, the uniform methods sometimes substantially underestimate the length of the tail of $g$ in these long-tailed scenarios, 
causing over-shrinkage of the tail toward 0.}
\end{subtable}

\begin{subtable}{\textwidth}
\centering\input{../analysis/table/scoverage_pos.tex}
\caption{``Significant" positive discoveries. Coverage rates are generally satisfactory, except for the symmetric methods under the asymmetric (``skew") scenario. }
\end{subtable}

@@

\begin{figure}
\begin{subfigure}{\textwidth}
\centering\includegraphics[width=4in]{figures/GOODPOOReg_hist.pdf} 
    \label{fig:goodpoor-hist}
    \caption{Density histograms of $p$ values for good-precision, poor-precision, and combined observations}
 \end{subfigure}
\begin{subfigure}{\textwidth}
\centering\includegraphics[width=4in]{figures/GOODPOOReg_scatter.pdf}
    \caption{Comparison of results of different methods applied to good-precision observations only ($x$ axis) and combined data ($y$ axis). Each point shows the ``significance" ($q$ values from \qvalue; $\lfdr$ for \locfdr; $\lfsr$ for \ashr) of a good-precision observation under the two different analyses.} \label{fig:goodpoor-scatter}
\end{subfigure}
\caption{Simulation illustrating how, for existing FDR methods, 
poor-precision observations can contaminate signal from good-precision observations. The top panel (a) illustrates that when 
$p$ values from good-precision observations (left) and from poor-precision observations (center) are combined (right), they produce
a distribution of $p$ values with less overall signal - and so, by conventional methods, will give a higher estimated FDR at any given threshold.
The bottom panel (b) illustrates this behaviour directly for the methods \qvalue and \locfdr: the $q$-values from \qvalue and the $\lfdr$ estimates from \locfdr are higher when applied to all data than when applied to good-precision observations only. In contrast the methods described here (\ashr) produce effectively the same results (here, the lfsr) in the good-precision and combined data analyses.} \label{fig:goodpoor}
\end{figure}

@@

\begin{figure}
\centering\includegraphics[width=4in]{figures/lfsr_vs_pval_GOODPOOR.pdf}
\caption{Figure illustrating affects of prior assumptions on re-ordering of significance. Left panel shows results under our ``default prior" which assumes that effects $\beta_j$ are identically distributed, independent of $s_j$. Right panel shows results under the ``$p$-value prior", which assumes that $z$ scores $\beta_j/s_j$ are identically distributed, independent of $s_j$.} \label{fig:lfsr_pval}
\end{figure}

@@

\begin{figure}
\begin{center}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_lfsr.Rmd/plot_lfsr_s_nn-1.pdf} 
\caption{Comparison of true and estimated $\lfsr$ when data are simulated with no point mass at zero ($\pi_0=0$), and also analyzed by \ashr with no point mass on 0 (and mixture of normal components for $g$). Black line is $y=x$ and red line is $y=2x$. The results illustrate how estimates of $\lfsr$ can be more accurate in this case. That is, assuming there is no point mass can be beneficial if that is indeed true.}  \label{fig:lfsr-nn}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{../analysis/figure/plot_lfsr.Rmd/plot_lfsr_s-1.pdf} 
\caption{Comparison of true and estimated $\lfsr$ when data are simulated with point mass at zero (drawn uniformly from [0,1] in each simulation), but analyzed by \ashr with no point mass on 0 (and mixture of normal components for $g$). Black line is $y=x$ and red line is $y=2x$. The results illustrate how estimates of $\lfsr$ can be anti-conservative if we assume there is no point mass when the truth is that there is a point mass.} \label{fig:lfsr-s}
\end{subfigure}
\end{center}
\caption{Illustration of effects of excluding a point mass from the analysis.} \label{fig:lfsr-nopointmass}
\end{figure}

@@

\begin{table}[!ht]
\begin{subtable}{\textwidth}
	\centering\input{../analysis/table/scoverage_all_nopen.tex}
	\caption{All observations}
\end{subtable}

\begin{subtable}{\textwidth}
\centering\input{../analysis/table/scoverage_neg_nopen.tex}
\caption{``Significant" negative discoveries.}
\end{subtable}

\begin{subtable}{\textwidth}
\centering\input{../analysis/table/scoverage_pos_nopen.tex}
\caption{``Significant" positive discoveries.}
\end{subtable}
